Appendix

### 2018-10-17 manuscript/appendix.Rmd
cleanup appendix, placeholder for milstead text

```{r recursive_partitioning_viz, echo=FALSE, eval=FALSE}
plot_tree(gettree(readRDS("../data/maxdepth_forest.rds")), 
          title = "Max Depth")

plot_tree(gettree(readRDS("../data/iws/cd_forest.rds")), 
          title = "Distance to Closest \n Upstream Lake (standardized)")
# inv_inv_closest(-1.51, nes_rf_iws) # 3773.614
plot_tree(gettree(readRDS("../data/nws/cd_forest.rds")), 
          title = "Distance to Closest \n Upstream Lake (standardized)")
# inv_inv_closest(-1.469, nes_rf_nws) # 2681.288

plot_tree(gettree(readRDS("../data/iws/sr_forest.rds")), 
          title = "Stream Order Ratio")
plot_tree(gettree(readRDS("../data/nws/sr_forest.rds")), 
          title = "Stream Order Ratio")

plot_tree(gettree(readRDS("../data/iws/linklength_forest.rds")), 
          title = "Link Length")
plot_tree(gettree(readRDS("../data/nws/linklength_forest.rds")), 
          title = "Link Length")

plot_tree(gettree(readRDS("../data/iws/uplakearea_forest.rds")), 
          title = "Upstream Lake Area")
# plot_tree(gettree(readRDS("01_Chapter/data/nws/uplakearea_forest.rds")), 
#           title = "Upstream Lake Area")

plot_tree(gettree(readRDS("../data/iws/baseflow_forest.rds")), 
          title = "Baseflow")

plot_tree(gettree(readRDS("../data/iws/wetland-cover_forest.rds")), 
          title = "Wetland Cover")

plot_tree(gettree(readRDS("../data/iws/streamdensity_forest.rds")), 
          title = "Stream Density")
```

```{r graphical_exploratory_analysis, echo=FALSE, message=FALSE, warning=FALSE, fig.height=8.4, fig.cap="Exploratory plots", eval=FALSE}
partition_splits <- read.csv("../figures/table_1.csv", stringsAsFactors = FALSE)

nes_iws$p_pnt_source <-  rowSums(cbind(nes_iws$p_pnt_source_muni,
                                       nes_iws$p_pnt_source_septic,
                                       nes_iws$p_pnt_source_industrial),
                                 na.rm = TRUE)

md_v_la <- ggplot(data = nes_iws) + 
  geom_point(aes(x = maxdepth, 
                 y = upstream_lakes_4ha_area_ha, color = lakeconnection)) +
  ylab("Upstream Lake Area (ha)") + xlab("Max Depth (m)") + 
  geom_vline(data = partition_splits, aes(
    xintercept = partition_splits$splits[
      partition_splits$pnames2 == "md" & partition_splits$scale == "focal"])) + 
  geom_hline(data = partition_splits, aes(
    yintercept = partition_splits$splits[
      partition_splits$pnames2 == "la" & partition_splits$scale == "nws"])) + 
  scale_y_log10()

md_v_ll_iws <- ggplot(data = nes_iws) + 
  geom_point(aes(x = maxdepth, 
                 y = link_length, color = lakeconnection)) +
  ylab("Link Length") + xlab("Max Depth (m)") + 
  geom_vline(data = partition_splits, aes(
    xintercept = partition_splits$splits[
      partition_splits$pnames2 == "md"])) + 
  geom_hline(data = partition_splits, aes(
    yintercept = partition_splits$splits[
      partition_splits$pnames2 == "ll" & partition_splits$scale == "iws"]))

md_v_ll_nws <- ggplot(data = nes_nws) + 
  geom_point(aes(x = maxdepth, 
                 y = avg_link_length, color = lakeconnection)) +
  ylab("Link Length") + xlab("Max Depth (m)") + 
  geom_vline(data = partition_splits, aes(
    xintercept = partition_splits$splits[
      partition_splits$pnames2 == "md"])) + 
  geom_hline(data = partition_splits, aes(
    yintercept = partition_splits$splits[
      partition_splits$pnames2 == "ll" & partition_splits$scale == "nws"]))

md_v_cd_nws <- ggplot(data = nes_nws) + 
  geom_point(aes(x = maxdepth, 
                 y = closest_lake_distance, color = lakeconnection)) +
  ylab("Closest Lake Distance") + xlab("Max Depth (m)") + 
  geom_vline(data = partition_splits, aes(
    xintercept = partition_splits$splits[
      partition_splits$pnames2 == "md"])) + 
  geom_hline(data = partition_splits, aes(
    yintercept = partition_splits$splits[
      partition_splits$pnames2 == "cd" & partition_splits$scale == "nws"]))

ll_v_cd_nws <- ggplot(data = nes_nws) + 
  geom_point(aes(x = avg_link_length, 
                 y = closest_lake_distance, color = lakeconnection)) +
  ylab("Closest Lake Distance") + xlab("Link Length") + 
  geom_vline(data = partition_splits, aes(
    xintercept = partition_splits$splits[
      partition_splits$pnames2 == "ll" & partition_splits$scale == "nws"])) + 
  geom_hline(data = partition_splits, aes(
    yintercept = partition_splits$splits[
      partition_splits$pnames2 == "cd" & partition_splits$scale == "nws"])) + 
  scale_x_log10() + scale_y_log10() + xlab("log(Link Length)") + ylab("log(cd)")

legend <- get_legend(md_v_la)

plot_grid(md_v_la + theme(legend.position = "none"), 
          md_v_ll_iws + theme(legend.position = "none"), 
          md_v_ll_nws + theme(legend.position = "none"),
          ll_v_cd_nws + theme(legend.position = "none"),
          ggplot() + geom_point(aes(nes_iws$hu12_baseflowindex_mean, nes_nws$baseflow, color = nes_iws$state %in% c("MAINE", "NEW HAMPSHIRE", "IOWA", "MISSOURI", "OHIO", "ILLINOIS"))) + 
            geom_hline(aes(yintercept = 53.43)) +
            geom_vline(aes(xintercept = 63.76)) + 
            ylab("NWS Baseflow") + xlab("IWS Baseflow") + 
            theme(legend.position = "none"),
          ggplot() + geom_point(aes(
            nes_iws$iws_streamdensity_streams_density_mperha, 
            nes_nws$stream_density, color = nes_iws$lakeconnection)) + 
            geom_hline(aes(yintercept = 10.4), color = "red") +
            geom_vline(aes(xintercept = 4.43), color = "red") +
            geom_abline(aes(slope = 1, intercept = 0)) + 
            ylab("NWS Stream Density") + xlab("IWS Stream Density") + 
            theme(legend.position = "none"),

          ggplot() + geom_point(aes(nes_iws$closest_lake_distance, 
                                    nes_nws$closest_lake_distance, 
                                    color = nes_iws$lakeconnection)) + 
            geom_hline(aes(yintercept = 2776.81), color = "red") +
            geom_vline(aes(xintercept = 3773.61), color = "red") +
            geom_abline(aes(slope = 1, intercept = 0)) +
            scale_x_log10() + 
            scale_y_log10() + 
            ylab("NWS Lake Distance") + xlab("IWS Lake Distance") + 
            theme(legend.position = "none"),
          ggplot(data = nes_iws) + 
            geom_point(aes(x = p_pnt_source / (p_nonpnt_source + p_pnt_source), 
                           y = p_percent_retention)) + 
            xlab("p_percent_pnt-source"), 
          ncol = 2)
```

```{r graphical_exploratory_analysis_cont, echo=FALSE, message=FALSE, warning=FALSE, fig.height=6.3, fig.cap="Exploratory plots cont", eval=FALSE}
lg <- lagosne_load("1.087.1")
nes_nws_temp <- dplyr::left_join(nes_nws, select(lg$iws, lagoslakeid, iws_ha))
nes_nws_temp$p_pnt_source <-  rowSums(cbind(nes_nws_temp$p_pnt_source_muni,
                                       nes_nws_temp$p_pnt_source_septic,
                                       nes_nws_temp$p_pnt_source_industrial),
                                 na.rm = TRUE)
nes_nws_sf    <- coordinatize(nes_nws_temp, "lat", "long")
us_states <- st_intersects(us_states(), nes_nws_sf)
us_states <- us_states()[unlist(lapply(us_states, function(x) length(x) > 0)),]

plot_grid(
ggplot() + geom_point(data = nes_nws_temp, 
                      aes(x = iws_ha, y = avg_link_length)) + 
  xlim(300, 100000) + ylab("Average Link Length") + 
  xlab("Interlake Watershed Area (ha)") + 
  geom_hline(aes(yintercept = 2380.09), color = "red"),

ggplot() + geom_point(data = nes_nws_temp, 
                      aes(x = iws_ha, y = closest_lake_distance)) + 
  xlim(300, 100000) + ylab("Closest Lake Distance") + 
  xlab("Interlake Watershed Area (ha)") + 
  geom_hline(aes(yintercept = 3273.65), color = "red"),

ggplot() + geom_point(data = nes_nws_temp, 
                      aes(x = iws_ha, y = p_percent_retention)) + 
  xlim(300, 100000) + ylab("P Retention") + 
  xlab("Interlake Watershed Area (ha)"),

ggplot() + geom_sf(data = us_states) + 
  geom_sf(data = nes_nws_sf, aes(color = p_pnt_source / (p_nonpnt_source + p_pnt_source))) + theme(legend.direction = "horizontal", legend.position = "bottom") + ggtitle("% pnt source P"),

ggplot() + geom_sf(data = us_states) + 
  geom_sf(data = nes_nws_sf, aes(color = log(maxdepth))) + theme(legend.direction = "horizontal", legend.position = "bottom") + ggtitle("max depth"), 
ggplot() + geom_sf(data = us_states) + 
  geom_sf(data = nes_nws_sf, aes(color = log(iws_ha))) + theme(legend.direction = "horizontal", legend.position = "bottom") + ggtitle("iws area"), 
ncol = 2)
```

```{r graphical_exploratory_analysis_cont_cont, echo=FALSE, message=FALSE, warning=FALSE, fig.height=5.3, fig.cap="Exploratory plots cont x 2", eval=FALSE}
lg <- lagosne_load("1.087.1")

nes_nws_temp <- nes_nws
nes_nws_temp$p_pnt_source <-  rowSums(cbind(nes_nws_temp$p_pnt_source_muni,
                                            nes_nws_temp$p_pnt_source_septic,
                                            nes_nws_temp$p_pnt_source_industrial),
                                      na.rm = TRUE)
nes_nws_sf    <- coordinatize(nes_nws_temp, "lat", "long")
us_states <- st_intersects(us_states(), nes_nws_sf)
us_states <- us_states()[unlist(lapply(us_states, function(x) length(x) > 0)),]

plot_grid(
  ggplot() + geom_point(data = nes_nws_temp, 
                        aes(x = nws_ha, y = upstream_lakes_4ha_area_ha)) + 
    xlim(300, 100000) + ylab("Up. Lk. Area") + 
    xlab("Network Watershed Area (ha)"),
  ggplot() + geom_point(data = nes_nws_temp, 
                        aes(x = nws_ha, y = stream_order_ratio)) + 
    xlim(300, 100000) + ylab("Stream Order Ratio") + 
    xlab("Network Watershed Area (ha)"),

  ggplot() + geom_point(data = nes_nws_temp, 
                        aes(x = nws_ha, y = p_percent_retention)) + 
    xlim(300, 100000) + ylab("P Retention") + 
    xlab("Network Watershed Area (ha)"),

  ggplot() + geom_point(data = nes_nws_temp, 
                        aes(x = nws_ha, 
                            y = p_pnt_source / (p_nonpnt_source + p_pnt_source))) + 
    xlim(300, 100000) + ylab("% Pnt Source") + 
    xlab("Network Watershed Area (ha)"), 
  ncol = 2)
```

```{r stream_density-vs-link_length, eval=FALSE}
test <- dplyr::select(nes_nws, 
              avg_link_length, 
              stream_density, 
              closest_lake_distance) %>%
dplyr::rename("Average Link Length" = avg_link_length,
              "Stream Density" = stream_density,
              "Closest Lake Distance" = closest_lake_distance) %>%
dplyr::mutate(`Closest Lake Distance` = `Closest Lake Distance` / 100, 
              `Average Link Length` = `Average Link Length` / 100)

pair_opts <- theme(axis.text = element_blank(), 
      axis.ticks = element_blank())

cowplot::plot_grid(
  ggplot(data = test) + 
    geom_point(aes(y = `Average Link Length`, x = `Stream Density`)) + 
    pair_opts,
  ggplot(data = test) + 
    geom_point(aes(y = `Average Link Length`, x = `Closest Lake Distance`)) + 
    ylab("") + pair_opts, 
  ggplot(data = test) + 
    geom_point(aes(y = `Closest Lake Distance`, x = `Stream Density`)) +
    pair_opts,
  ggplot() + geom_blank(),
  nrow = 2, ncol = 2)
```

```{r conceptual_summary, echo=FALSE, fig.cap="Connectivity metric effects on lake processing.", eval=FALSE}
dt <- data.frame(
  rbind(
    c("closest lake distance", "lower", "higher", "lower", "higher", "lake-stream", "long"), 
    c("average link length", "lower", "higher", "lower", "higher", "stream", "long"), 
    c("lakeconnection", "DR_Stream", "higher", "lower", "higher", "lake", "long"), 
    c("upstream lake area", "lower", "higher", "lower", "higher", "lake", "lat"), 
    c("stream density", "higher", "higher", "lower", "higher", "stream", "lat"),
    c("baseflow", "higher", "higher", "lower", "higher", "stream", "lat"), 
    c("stream order ratio", "higher", "higher", "lower", "higher", "stream", "long")))

names(dt) <- c("metric", "direction", "k", "connectivity", "in_lake_processing", "axis", "connectivity type")

knitr::kable(dt)
```

@@

```{r load_packages, echo=FALSE}

@@

```{r iws_vs_nws-gis, cache=TRUE, echo=FALSE, warning=FALSE, message=FALSE, eval=FALSE}
# lagoslakeid <- 6302
# iws <- pull_iws(lagoslakeid, maxsteps = Inf)
# nws <- pull_nws(lagoslakeid, maxsteps = Inf)
# nws_lakes <- pull_lakes(nws)
# saveRDS(iws, "../data/iws_extent.rds")
# saveRDS(nws, "../data/nws_extent.rds")
# saveRDS(nws_lakes, "../data/nws_lakes.rds")

iws <- readRDS("../data/iws_extent.rds")
nws <- readRDS("../data/nws_extent.rds")
nws_lakes <- readRDS("../data/nws_lakes.rds")

nws_lakes <- nws_lakes[order(st_area(nws_lakes), decreasing = TRUE),]
nws_lakes <- nws_lakes[1:2,]

iws_outline <- concaveman(st_cast(iws, "POINT"))
nws_outline <- concaveman(st_cast(nws, "POINT"))
lake_1_outline <- concaveman(st_cast(nws_lakes[1,], "POINT"))
lake_2_outline <- concaveman(st_cast(nws_lakes[2,], "POINT"))

ggplot() + 
  geom_sf(data = nws_outline, color = "yellow", size = 2) + 
  geom_sf(data = iws_outline, color = "cyan", size = 2) + 
  geom_sf(data = nws) +
  geom_sf(data = lake_1_outline, color = "cyan") +
  geom_sf(data = lake_2_outline, color = "yellow") +
  coord_sf(crs = st_crs(nws), datum = NA) + 
  # geom_sf(data = iws) + 
  theme_void()

```{r best_partition_maps, cache=TRUE, echo=FALSE, message=FALSE, warning=FALSE, eval=FALSE}
library(tmap)
library(sf)
library(LAGOSNE)
library(USAboundaries)
library(dplyr)

results_table <- read.csv("../scripts/table_1.csv", stringsAsFactors = FALSE)
ll_split <- dplyr::filter(results_table, 
                          nws_names == "avg_link_length" & 
                          scale == "nws")$splits

nes_nws <- mutate(nes_nws, grp = ifelse(avg_link_length > ll_split, 
                                  "High", "Low"))

nes_sf    <- coordinatize(nes_nws, "lat", "long")
us_states <- st_intersects(us_states(), nes_sf)
us_states <- us_states()[unlist(lapply(us_states, function(x) length(x) > 0)),]

us <- USAboundaries::us_boundaries()
us <- us[unlist(lapply(st_intersects(us, nes_sf), function(x) length(x) > 0)),]
us <- filter(us, stusps != "AR")

nes_extent <- group_by(us, jurisdiction_type)
nes_extent <- st_union(nes_extent)
nes_extent <- as_Spatial(nes_extent)

palette <- c("black",
              "black")

m_nes <-  tm_shape(us) + tm_polygons() +
          tm_shape(nes_extent) + tm_borders(lwd = 3) +
          tm_shape(dplyr::filter(nes_sf, !is.na(grp))) + tm_dots("grp", palette = palette,
                                 size = 0.2, legend.show = FALSE, 
                                 title = "Average Link Length") +
          # tm_credits("National Eutrophication Survey") +
          tm_layout(frame = FALSE,
                    legend.outside = FALSE,
                    legend.stack = "horizontal")

save_tmap(m_nes, "../figures/best_partition_maps-1.png",
          scale = 0.7, width = 3.125)

# # # # #

palette <- c(viridis::viridis(1, begin = 0),
             viridis::viridis(1, begin = 0.5))

m_nes <- tm_shape(us) + tm_polygons() +
          tm_shape(nes_extent) + tm_borders(lwd = 3) +
          tm_shape(dplyr::filter(nes_sf, !is.na(grp))) + tm_dots("grp", palette = palette,
                                 size = 0.2, legend.show = TRUE, 
                                 title = "Average Link Length") +
          # tm_credits("National Eutrophication Survey") +
          tm_layout(frame = FALSE,
                    legend.outside = FALSE,
                    legend.stack = "horizontal")

save_tmap(m_nes, "../figures/best_partition_maps-2.png",
          scale = 0.7, width = 3.125)
```

```{r plot_tree_example, echo=FALSE, fig.width=2, fig.height=3, eval=FALSE, eval=FALSE}
plot_tree(gettree(readRDS("../data/nws/linklength_forest.rds")), 
          title = "Link Length")
```

```{r partition_example_scatter, fig.height=4, fig.width=4.2, warning=FALSE, eval=FALSE}
# setwd("manuscript")
results_table <- read.csv("../scripts/table_1.csv", stringsAsFactors = FALSE)
ll_split <- dplyr::filter(results_table, 
                          nws_names == "avg_link_length" & 
                          scale == "nws")$splits

nes_nws <- mutate(nes_nws, grp = ifelse(avg_link_length > ll_split, 
                                  "Higher", "Lower"))

ggplot(data = dplyr::filter(nes_nws, 
                     !is.na(avg_link_length))) + 
         geom_point(aes(x = avg_link_length, 
                                        y = p_percent_retention, 
                                        color = grp), 
                                    size = 1.3) + 
  scale_color_manual(values = c(viridis::viridis(1, begin = 0), 
                     viridis::viridis(1, begin = 0.5))) +
  ylab("P Retention") + xlab("Avg. Link Length") + 
  geom_vline(xintercept = ll_split) + 
  theme(legend.position = "none") 
```

```{r 05_partition_vollenweider, echo=FALSE, fig.cap="Residence time (yr) versus P retention for the NES dataset and hierarchical model fits to the data where the solid lines and shaded intervals represent the median and central 95% model  estimates respectively. The green lines and symbols are the estimates from the lower of the two partition groups while the purple lines are estimates for the upper of the two partition groups (see Table 2).", fig.width = 4.8, fig.height=5, warning=FALSE, eval=FALSE}

knitr::include_graphics("../figures/05_partition_vollenweider-1.pdf")
```

```{r milstead_reanalysis, fig.cap="Relationship between residence time and phosphorus retention for inland lakes with surface area greater than 4 ha in Northeastern USA (New England). Vertical dashed lines denote lakes with intermediate residence times (within the interquartile range). Best fit lines are colored based on whether they have upstream lake connections (DR_LakeStream), or upstream stream connection (DR_Stream), are headwater lakes, or are isolated lakes. Data from Milstead et al. (2013).", fig.width = 5, fig.height = 4}
library(cowplot)
library(ggplot2)
library(sf)
library(nhdR)
library(LAGOSNE)
library(maps)
library(dplyr)

@@

# milstead <- droplevels(milstead[milstead$lakeconnectivity != "Isolated",])
gg_fit_multi <- ggplot(data = md, aes(x = hrt, y = Rp)) +
  geom_point(size = 0.9) +
  scale_x_log10(labels = mixed_labels, 
                breaks = as.numeric(yr_labels), limits = c(1 / 365, 11)) +
  stat_smooth(method = "glm", method.args = list(family = "binomial"), 
              se = TRUE, aes(color = lakeconnection), 
              data = md) +
  scale_color_brewer(palette = "Set1") +
  cowplot::theme_cowplot() + 
  theme(legend.title = element_blank(), legend.position = c(0.13, 0.8),
        legend.text = element_text()) +
  xlab("Residence Time") +
  ylab("P Retention (%)") + 
  geom_segment(data = data.frame(x = quants[c(2, 4)], y = c(0.8, 0.8)), 
               aes(x = x, y = c(0, 0), xend = x, yend = y), 
               color = "gray42", size = 1.5, linetype = 2)

# if(!interactive()){  
  gg_fit_multi
# }

# legend <- get_legend(gg_fit_multi)
# gg <- plot_grid(gg_fit_single, gg_fit_multi, scale = c(1, 1), rel_widths = c(3, 3), nrow = 1)
# 
# if(!interactive()){
#   ggsave("milstead_conny.pdf", gg, height = 3.5, width = 7)
# }

# ggsave("milstead_conny_nogroup.pdf", gg)

# hist(log(x))
# hist(log(dt[dt$variable == "x_raw", "value"]))

# nes <- read.csv("/home/jose/R/scripts/NES/nes_data.csv")
# nes <- nes[!is.na(nes$retention_time),] 
# 
# nes$retention_time[nes$retention_time_units == "days" & 
#   !is.na(nes$retention_time_units)] <- 
#   nes$retention_time[nes$retention_time_units == "days" & 
#                        !is.na(nes$retention_time_units)] / 365
# 
# dt <- data.frame(variable = "Milstead", 
#           reshape2::melt(milstead[,"hrt"]))
# 
# # quants <- exp(quantile(log(dt$value)))
# # format_labels(quants, 365)
# # format_labels(quants, 12)
# 
# dt <- rbind(dt, 
#         data.frame(variable = "NES", 
#           reshape2::melt(nes[, c("retention_time")])))  
# 
# # dt$value <- log(dt$value)
# 
# dens <- density(dt[dt$variable == "Milstead", "value"])
# dens <- data.frame(x = dens$x, y = dens$y)
# 
# gg <- ggplot(data = dt, aes(x = value)) +
#   geom_density(aes(linetype = variable), alpha = 0.5, size = 1.55) + 
#   scale_x_log10(breaks = as.numeric(yr_labels)[c(3, 5, 7)], 
#                 labels = mixed_labels[c(3, 5, 7)]) + 
#   cowplot::theme_cowplot() + theme(legend.position = c(0.15, 0.8), legend.title = element_blank(), legend.text = element_text()) +
#   xlab("Residence Time") + 
#   geom_segment(data = data.frame(x = quants[c(2, 4)], y = c(0.266, 0.48)), 
#                aes(x = x, y = 0, xend = x, yend = y), size = 1.55)
# 
# if(!interactive()){  
#   ggsave("hrt_density.pdf", gg, height = 4)
# }
# 
# # nes_fit_single <- ggplot(data = nes, aes(x = retention_time, y = p_percent_retention)) +
# #   geom_point() +
# #   scale_x_log10(labels = mixed_labels[c(2:4)], breaks = c(1e-05, 1e-02, 1e+01)) +
# #   stat_smooth(method = "glm", method.args = list(family = "binomial"), se = TRUE) +
# #   scale_color_brewer(palette = "Set1") +
#   cowplot::theme_cowplot() + 
#   theme(legend.position = "none", legend.title = element_blank(), legend.text = element_text()) +
#   xlab("Residence Time") +
#   ylab("P Retention (%)")
```

```{r p-retention_vs_percent-ag, fig.cap="P retention versus percent agriculture in network watersheds.", fig.width = 3, fig.height = 3}
nes_nws$percent_ag <- nes_iws$iws_nlcd1992_pct_81 + nes_iws$iws_nlcd1992_pct_82

@@

```{r nes_vs_nla, fig.cap="Comparison of selected lake characteristics among the stratified random sampling design of the National Lakes Assessment (nla) and the haphazard sampling of the National Eutrophication Survey (nes) lakes analyzed in the present study.", fig.height=4}
# , message=FALSE, warning=FALSE
nla <- nla_load(2012)

>>>>

@@

```{r load_packages, echo=FALSE, warning=FALSE, message=FALSE}

@@

milstead reanalysis

```{r milstead_reanalysis, fig.cap="Relationship between residence time and phosphorus retention for inland lakes with surface area greater than 4 ha in Northeastern USA (New England). Vertical dashed lines denote lakes with intermediate residence times (within the interquartile range). Best fit lines are colored based on whether they have upstream lake connections (DR_LakeStream), or upstream stream connection (DR_Stream), are headwater lakes, or are isolated lakes. Data from Milstead et al. (2013).", fig.width = 5, fig.height = 4, warning=FALSE, message=FALSE}
library(cowplot)
library(ggplot2)
library(sf)
library(nhdR)
library(LAGOSNE)
library(maps)
library(dplyr)

@@

# milstead <- droplevels(milstead[milstead$lakeconnectivity != "Isolated",])
gg_fit_multi <- ggplot(data = md, aes(x = hrt, y = Rp)) +
  geom_point(size = 0.9) +
  scale_x_log10(labels = mixed_labels, 
                breaks = as.numeric(yr_labels), limits = c(1 / 365, 11)) +
  stat_smooth(method = "glm", method.args = list(family = "binomial"), 
              se = TRUE, aes(color = lakeconnection), 
              data = md) +
  scale_color_brewer(palette = "Set1") +
  cowplot::theme_cowplot() + 
  theme(legend.title = element_blank(), legend.position = c(0.13, 0.8),
        legend.text = element_text(), legend.background = element_rect(fill = "white")) +
  xlab("Residence Time") +
  ylab("P Retention (%)") + 
  geom_segment(data = data.frame(x = quants[c(2, 4)], y = c(0.8, 0.8)), 
               aes(x = x, y = c(0, 0), xend = x, yend = y), 
               color = "gray42", size = 1.5, linetype = 2)

gg_fit_multi
```

```{r p-retention_vs_percent-ag, fig.cap="P retention versus percent agriculture in network watersheds.", fig.width = 3, fig.height = 3, warning=FALSE, message=FALSE}
nes_nws$percent_ag <- nes_iws$iws_nlcd1992_pct_81 + nes_iws$iws_nlcd1992_pct_82

@@

```{r nes_vs_nla, fig.cap="Comparison of selected lake characteristics among the stratified random sampling design of the National Lakes Assessment (nla) and the haphazard sampling of the National Eutrophication Survey (nes) lakes analyzed in the present study.", fig.height=4, warning=FALSE, message=FALSE}
# , message=FALSE, warning=FALSE
nla <- nla_load(2012)
